---
title: "M8W4 - Practical Machine Learning - Course Project"
author: "Thomas Goeppert"
date: "16 5 2020"
output:
  html_document: default
  pdf_document: default
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

## Libraries

```{r, message = FALSE, warning = FALSE}

library(readr)
library(dplyr)
library(tidyverse)
library(caret)
library(rpart)
library(rattle)
library(corrplot)
library(rpart)
library(rpart.plot)

```

## Loading & prepare Data

```{r}

# Read Data


pml_training <- read.csv('C:/temp/Coursera/M8W4/pml-training.csv', header=T)

pml_valid <- read.csv('C:/temp/Coursera/M8W4/pml-testing.csv', header=T)

str(pml_training)

# Delete Index Row & TimeStamp

pml_training <- pml_training[,-c(1,3,4,5)]

# Create Training and Testing Partition

set.seed(271184)
index_Part <- as.vector(createDataPartition(pml_training$classe, p = .8, list = FALSE))
                      
head(index_Part)

pml_training <- pml_training[index_Part,]

pml_testing <- pml_training[-index_Part,]

# Delete Data with almost no variance

delete_NZV <- nearZeroVar(pml_training)

pml_training <- pml_training[,-delete_NZV]

# #DIV/0 ersetzen druch NA

pml_training[pml_training=="#DIV/0!"] <- NA

# Delete column when more than 30 % are NA

delete_NA <- c()

for(i in 1:length(pml_training)){
  if (sum(is.na(pml_training[,i])) /  length(pml_training[,i]) >= 0.3){
      delete_NA <- c(delete_NA, i)
    }
}

pml_training <- pml_training[,-delete_NA]


```

## EDA for Training Data

```{r}
 


# Filter numeric values

num <- c()

for(i in 1:length(pml_training)){
  
    if (is.numeric(pml_training[,i])){
      num <- c(num, i)
    }
}

pml_training_Numeric <- pml_training[,num]

# Check and visualize the correlation

corr <-cor(pml_training_Numeric)

corrplot(corr, order = "FPC", method = "color", type = "upper", 
         tl.cex = 0.6, tl.col = "black")

```

## Train different Models and check which fits best

```{r}
 
# Decission Tree

set.seed(271184)

model_DT <- rpart(classe ~ ., data=pml_training)

rpart.plot(model_DT)

predict_DT <- predict(model_DT, pml_testing, type = "class", verbose = FALSE)

C_Matrix <- confusionMatrix(predict_DT, pml_testing$classe)

C_Matrix$overall[1]

# Accuray quite OK lets check the others
# more Details attached

C_Matrix

# Random Forest

set.seed(271184)


control_RF <- trainControl(method="cv", number=2)

model_RF <- train(classe ~ ., data=pml_training, method="rf", verbose = FALSE)

predict_RF <- predict(model_RF, pml_testing)

C_Matrix <- confusionMatrix(predict_RF, pml_testing$classe)

C_Matrix$overall[1]

# Accuray of 1!, there might be some overfitting
# more details attached

C_Matrix


# G. Boosted Reg. Model

set.seed(271184)

control_GBM <- trainControl(method = "repeatedcv", number = 2, repeats = 1)

model_GBM <- train(classe ~ ., data=pml_training, method="gbm", trControl = control_GBM, verbose = FALSE)

predict_GBM <- predict(model_GBM, pml_testing)

C_Matrix <- confusionMatrix(predict_GBM, pml_testing$classe)

C_Matrix$overall[1]

# Accuray is quite high but not as goog as RF
# more details attached

C_Matrix

```

# Choose Model and Predict the Data

```{r}
# Choose RF to predict as it hast the highest accuracy

predict_DT <- predict(model_RF, pml_valid, verbose = FALSE)

# My prediction is

predict_DT

```